---
title: "Meta-analysis of synesthetic metaphor tables"
author: "Bodo"
date: "2023-07-10"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This script looks at percent hierarchy consistency. Since this is our first analysis, we'll also spend some time checking datasets to report overall statistics in the paper.

# Setup

```{r warning = FALSE, message = FALSE}
library(tidyverse)     # for data processing and visualization
library(brms)          # for fitting bayesian models
library(tidybayes)     # for spread_draws()
```

Show R and package versions for computational reproducibility and reporting in paper:

```{r}
packageVersion('tidybayes')
```

Load the `both_tables` list that has been created in the `table_preprocessing.Rmd` file.

```{r warning = FALSE, message = FALSE}
# List of all tables:

load('../additional_data/all_included_tables_list.RData')
```

Show 5 random rows each to get an overview:

```{r}
# List of all tables:

both_tables[sample(1:length(both_tables), 5)]
```

Load metadata and rename columns as desired:

```{r warning = FALSE, message = FALSE}
metadata <- read_csv('../metadata.csv') %>% 
  rename(genre = Genre,
         language = `Language of data`,
         source = `Type of data source`,
         table_title = `Table title`)
```

# Compute source/target ratios

Let's compute the source-target ratios. This is a fairly intuitive quantity: for touch, for example, we look at the row totals — how often it is used as a source — and divide this by the column totals — how often it us used as a target. The corresponding ratio quantifies how much more something is used as a source.

```{r}
# Setup tibble with empty columns:

ratios <- tibble(dataset = names(both_tables),
                 touch = NA,
                 taste = NA,
                 smell = NA,
                 sight = NA,
                 sound = NA)

# Loop through tables, compute proportions, and save in results table:

for (i in seq_along(both_tables)) {
  # Extract table from list and transform into matrix object without first column:
  
  M <- both_tables[[i]]
  
  # All ratios:
  
  these_ratios <- rowSums(M, na.rm = TRUE) / colSums(M, na.rm = TRUE)
  
  # Get the hierarchy consistent cases and divide by sum:
  
  ratios[i, ]$touch <- these_ratios['touch']
  ratios[i, ]$taste <- these_ratios['taste']
  ratios[i, ]$smell <- these_ratios['smell']
  ratios[i, ]$sound <- these_ratios['hearing']
  ratios[i, ]$sight <- these_ratios['sight']
}
```

Check table:

```{r}
ratios
```

The `Inf` cases result from division by zero for cases where something is only used as a source, but never as a target (= 0). Let's set these to `NA` as the true ratio cannot be known in this case.

```{r}
# Define helper function:

inf_to_NA <- function(x) ifelse(is.infinite(x), NA, x)

# Apply this function to all numeric ("double") columns:

ratios <- ratios %>%
  mutate(across(where(is.double), inf_to_NA))

# Check:

ratios
```

Seems to have worked.

Make that into a long format table so we can plot it:

```{r}
ratios_long <- ratios %>% 
  pivot_longer(cols = touch:sound,
               names_to = 'modality',
               values_to = 'ratio')

# Check:

ratios_long
```

We'll later use log ratios as well for plotting (ratios can easily get skewed if the denominators are small, making it hard to see patterns).

```{r}
ratios_long <- mutate(ratios_long,
                      log_ratio = log(ratio),
                      log_ratio = inf_to_NA(log_ratio))
```

# Ratio averages and plots

Check averages:

```{r}
ratios_long %>% 
  group_by(modality) %>% 
  summarize(mean_ratio = mean(ratio, na.rm = TRUE),
            log_ratio = mean(log_ratio, na.rm = TRUE))
```

Make the order of the `modality` factor roughly correspond to the hierarchy for plotting purposes:

```{r}
# Define vector with desired order:

level_order <- c('touch', 'taste', 'smell', 'sight', 'sound')

# Make column into factor with those levels:

ratios_long <- mutate(ratios_long,
                      modality = factor(modality,
                                        levels = level_order))
```

Make a plot of this:

```{r}
# Core of plot:

ratio_p <- ratios_long %>% 
  ggplot(aes(x = modality,
             y = log_ratio,
             fill = modality)) +
  geom_hline(yintercept = 0, linetype = 'dashed') +
  geom_boxplot(width = 0.5)

# Add annotations, axes, labels to plot:

ratio_p <- ratio_p +
  xlab(NULL) +
  ylab('Log source/target ratio') +
  scale_fill_viridis_d(option = 'D') +
  scale_y_continuous(limits = c(-6, 6),
                     breaks = seq(-6, 6, 2))

# Cosmetic tweaking:

ratio_p <- ratio_p +
  theme_classic() +
  theme(legend.position = 'none',
        axis.text.x = element_text(face = 'bold'),
        axis.title = element_text(face = 'bold',
                                  size = 12),
        axis.title.y = element_text(margin = margin(r = 10)))

# Show plot in markdown and also save externally outside of R:

ratio_p
ggsave(plot = ratio_p,
       filename = '../figures/pdf/source_target_ratios.pdf',
       width = 5.2, height = 4.5)
ggsave(plot = ratio_p,
       filename = '../figures/png/source_target_ratios.png',
       width = 5.2, height = 4.5)
```

# Bayesian model of ratios

How are the log ratios themselves distributed? This could inform a choice of model.

```{r}
ratios_long %>% 
  ggplot(aes(x = log_ratio)) +
  geom_density(fill = 'purple') +
  theme_classic()
```

Ok, I wouldn't be too opposed to using a Gaussian model in this case as a first pass, and see how far we can go with this. We should add the language metadata to the table though so that we can have a language random effect.

```{r}
ratios_long <- left_join(ratios_long,
                         select(metadata, table_title, genre, language),
                         by = c('dataset' = 'table_title'))
```

Set priors. Since we'll have random slopes for this model (each language has five data points now, one per modality, so we can fit by-language modality random slopes), we now also need LKJ priors for the random effects correlation matrix.

```{r}
my_priors <- c(prior(normal(0, 1), class = Intercept),
               prior(normal(0, 1), class = b),
               prior(student_t(3, 0, 2.5), class = sd), # df = 3, mu = 0, sigma = 2.5
               prior(lkj(2), class = cor))
```

Fit a Gaussian model then:

```{r eval = TRUE}
ratio_mdl <- brm(log_ratio ~ 
                  
                  # Fixed effects:
                  
                  1 + modality +
                  
                  # Random effects:
                  
                  (1 + modality|language),
                
                data = ratios_long,
                family = gaussian,
                
                # Priors:
                
                prior = my_priors,
                
                # MCMC settings:
                
                seed = 42,
                cores = 4,
                chains = 4,
                iter = 6000,
                warmup = 4000,
                control = list(adapt_delta = 0.99),
                save_pars = save_pars(all = TRUE))

# Save the model:

save(ratio_mdl, file = '../models/ratio_model.RData')
```

Load the pre-compiled model:

```{r}
load('../models/ratio_model.RData')
```

Assess whether this is a plausible data-generating process:

```{r}
pp_check(ratio_mdl, ndraws = 100)
```

Looks quite good!

Check the model:

```{r}
ratio_mdl
```

Touch is the reference level in the intercept. We can test whether taste, smell, sight and sound differ in terms of their source-target ratios, and how uncertain those differences are.

```{r}
hypothesis(ratio_mdl, 'modalitytaste > 0')
hypothesis(ratio_mdl, 'modalitysmell < 0')
hypothesis(ratio_mdl, 'modalitysight < 0')
hypothesis(ratio_mdl, 'modalitysound < 0')
```

We can also look at whether the smell coefficient differed reliably from the sight and sound coefficients, and from each other.

```{r}
hypothesis(ratio_mdl, 'modalitysmell < modalitytaste')
hypothesis(ratio_mdl, 'modalitytaste > modalitysmell')
hypothesis(ratio_mdl, 'modalitysmell < modalitysight')
hypothesis(ratio_mdl, 'modalitysmell > modalitysound')
hypothesis(ratio_mdl, 'modalitysight > modalitysound')
```

Or whether each condition is above zero.

```{r}
hypothesis(ratio_mdl, 'Intercept > 0') # touch
hypothesis(ratio_mdl, 'Intercept + modalitytaste  > 0') # taste
hypothesis(ratio_mdl, 'Intercept + modalitysmell  < 0') # smell
hypothesis(ratio_mdl, 'Intercept + modalitysight  < 0') # sight
hypothesis(ratio_mdl, 'Intercept + modalitysound  < 0') # sound
```

We can compare this to a model that only knows about whether the sense is lower or higher, thus collapsing sight/sound under higher and touch/taste/smell under lower. If this model performs worse, then this is evidence that it's better to look at specific modalities.

```{r}
ratios_long <- ratios_long %>% 
  mutate(hierarchy = ifelse(modality %in% c('sight', 'sound'),
                            'higher', # if
                            'lower')) # else

# Check:

ratios_long
```

The new `hierarchy` column encodes just this information. We can refit the model with `hierarchy` rather than `modality` as predictor.

```{r eval = TRUE}
ratio_hierarchy_mdl <- brm(log_ratio ~ 
                  
                  # Fixed effects:
                  
                  1 + hierarchy +
                  
                  # Random effects:
                  
                  (1 + hierarchy|language),
                
                data = ratios_long,
                family = gaussian,
                
                # Priors:
                
                prior = my_priors,
                
                # MCMC settings:
                
                seed = 42,
                cores = 4,
                chains = 4,
                iter = 6000,
                warmup = 4000,
                control = list(adapt_delta = 0.99),
                save_pars = save_pars(all = TRUE))

# Save the model:

save(ratio_hierarchy_mdl,
     file = '../models/ratio_hierarchy_model.RData')
```

Load the pre-compiled model:

```{r}
load('../models/ratio_hierarchy_model.RData')
```

The intercept is the ratio for touch, which is the reference level here. We can then test the hypothesis that the modality-specific model is better than the coarser low/high model. We can do this two ways, one using Bayes factors, another one using LOO-CV (leave-one-out cross-validation). Let's do the latter first:

```{r eval = TRUE}
# Individual LOO-ICs:

ratio_loo <- loo(ratio_mdl, moment_match = TRUE)
ratio_hierarchy_loo <- loo(ratio_hierarchy_mdl, moment_match = TRUE)

# Save:

save(ratio_loo, file = '../models/ratio_loo.RData')
save(ratio_hierarchy_loo, file = '../models/ratio_hierarchy_loo.RData')

# Compare:

ratio_loo_comparison <- loo_compare(ratio_loo, ratio_hierarchy_loo)


save(ratio_loo_comparison, file = '../models/ratio_loo_comparison.RData')
```

Load and show:

```{r}
load('../models/ratio_loo.RData')
load('../models/ratio_hierarchy_loo.RData')
load('../models/ratio_loo_comparison.RData')

# Show:

ratio_loo
ratio_hierarchy_loo
ratio_loo_comparison
```

The ratio model performs best, i.e., the modality-specific model is better in terms of cross-validation accuracy / it would generalize to unseen data better.

The difference in R-squared is what?

```{r}
# Bayes R2:

R2_ratio_mdl <- bayes_R2(ratio_mdl)
R2_ratio_hierarchy_mdl <- bayes_R2(ratio_hierarchy_mdl)

# Show:

R2_ratio_mdl
R2_ratio_hierarchy_mdl

# Difference:

R2_ratio_mdl[1] - R2_ratio_hierarchy_mdl[1]
```

45.6% more explained variance.

# New plot with model

Get the posterior samples from the model:

```{r}
posts <- ratio_mdl |> 
  spread_draws(b_Intercept, b_modalitytaste,
               b_modalitysmell, b_modalitysight,
               b_modalitysound)
```

Fill out the regression equation for all five cells of the stats:

```{r}
posts <- posts |> 
  mutate(taste = b_Intercept + b_modalitytaste,
         smell = b_Intercept + b_modalitysmell,
         sight = b_Intercept + b_modalitysight,
         sound = b_Intercept + b_modalitysound) |> 
  rename(touch = b_Intercept) |> 
  select(-(b_modalitytaste:b_modalitysound),
         -(.chain:.draw))

# Show:

posts
```

Compute relevant stats... need to make it long format for that:

```{r}
posts_long <- posts |>
  pivot_longer(cols = touch:sound,
               names_to = 'modality',
               values_to = 'log_ratio') |> 
  arrange(modality)

# Show long format:

posts_long
```

Compute 95% credible interval and means:

```{r}
fixefs <- posts_long |> 
  group_by(modality) |> 
  summarize(lower_CI = quantile(log_ratio, 0.025),
            upper_CI = quantile(log_ratio, 0.975),
            estimate = mean(log_ratio))

# Show:

fixefs
```

Make a beeswarm or violin plot:

```{r}
# Core of plot:

ratio_p <- ratios_long %>% 
  ggplot(aes(x = modality)) +
  geom_hline(yintercept = 0, linetype = 'dashed') +
  geom_violin(aes(y = log_ratio),
              alpha = 0,
              color = NA) +
  geom_violin(aes(fill = modality,
                    y = log_ratio),
              alpha = 0.7,
              linewidth = 0.3) +
  geom_errorbar(data = fixefs,
                mapping = aes(x = modality,
                              ymin = lower_CI, ymax = upper_CI),
                linewidth = 0.45,
                width = 0.15) +
  geom_point(pch = 15, size = 2.2,
             data = fixefs,
             mapping = aes(y = estimate))

# Add annotations, axes, labels to plot:

ratio_p <- ratio_p +
  coord_cartesian(clip = 'off') +
  xlab(NULL) +
  ylab('Log source/target ratio') +
  scale_fill_viridis_d(option = 'D') +
  scale_y_continuous(limits = c(-6, 6),
                     breaks = seq(-6, 6, 2)) +
  annotate('text',
           label = 'source preference',
           x = 5.55, hjust = 0.5,
           y = (0.55 + 5.2) / 2, size = 2.3,
           angle = 90) +
  annotate('text',
           label = 'target preference',
           x = 5.55, hjust = 0.5, angle = 90,
           y = (-0.55 + -5.2) / 2, size = 2.3) +
  annotate('segment', y = 0.55, yend = 5.2,
           x = 5.65, xend = 5.65,
           arrow = arrow(type = 'closed', length = unit(0.036, 'npc'))) +
  annotate('segment', y = -0.55, yend = -5.2,
           x = 5.65, xend = 5.65,
           arrow = arrow(type = 'closed', length = unit(0.036, 'npc')))

# Cosmetic tweaking:

ratio_p <- ratio_p +
  theme_classic() +
  theme(legend.position = 'none',
        axis.text.x = element_text(face = 'bold'),
        axis.title = element_text(face = 'bold',
                                  size = 12),
        axis.title.y = element_text(margin = margin(r = 10)),
        plot.margin = margin(r = 20))

# Show plot in markdown and also save externally outside of R:

ratio_p
ggsave(plot = ratio_p,
       filename = '../figures/pdf/source_target_ratios_violin_with_95CI.pdf',
       width = 5.2, height = 3.5)
ggsave(plot = ratio_p,
       filename = '../figures/png/source_target_ratios_violin_with_95CI.png',
       width = 5.2, height = 3.5)
```

# Hypotheses tests for conditions

With the new `posts` object, we can easily perform hypothesis tests to look at which modalities differ reliably in their source/target ratio means.

```{r}
# Touch against rest:

sum(with(posts, touch > taste)) / nrow(posts)
sum(with(posts, touch > smell)) / nrow(posts)
sum(with(posts, touch > sight)) / nrow(posts)
sum(with(posts, touch > sound)) / nrow(posts)

# Taste against rest:

sum(with(posts, taste > smell)) / nrow(posts)
sum(with(posts, taste > sight)) / nrow(posts)
sum(with(posts, taste > sound)) / nrow(posts)

# Smell against rest:

sum(with(posts, smell < sight)) / nrow(posts) # smell lower than sight
sum(with(posts, smell > sound)) / nrow(posts)

# Sight against rest:

sum(with(posts, sight > sound)) / nrow(posts)
```

# Calculate target entropy

Let's calculate the entropy to get a measure of the diversity of targets across cells. We will add +1 to get rid of `Inf` for those cases that are zero. Since this is applied to *all* cells, it shouldn't bias the results with respect to any one modality.

```{r}
# Setup tibble with empty columns:

entropies <- tibble(dataset = names(both_tables),
                    touch = NA,
                    taste = NA,
                    smell = NA,
                    sight = NA,
                    sound = NA)

# Vector of modalities:

mods <- c('touch', 'taste', 'smell', 'sight', 'sound')

# Loop through tables, compute proportions, and save in results table:

for (i in seq_along(both_tables)) {
  # Extract table from list and transform into matrix object without first column:
  
  M <- both_tables[[i]]
  
  # All ratios:
  
  for (j in 1:nrow(M)) {
    this_row <- M[j, ]
    this_row <- this_row[!is.na(this_row)]
    this_row <- this_row + 1 # to get rid of Inf for log
    ps <- this_row / sum(this_row)
    entropies[i, mods[j]] <- sum(ps * log(ps)) * -1
  }
}
```

Make that into a long format table so we can plot it:

```{r}
entro_df <- entropies %>% 
  pivot_longer(cols = touch:sound,
               names_to = 'modality',
               values_to = 'entropy')

# Check:

entro_df
```

Check averages:

```{r}
entro_df %>% 
  group_by(modality) %>% 
  summarize(M = mean(entropy, na.rm = TRUE)) |> 
  arrange(desc(M))
```

Make the order of the `modality` factor roughly correspond to the hierarchy for plotting purposes:

```{r}
# Define vector with desired order:

level_order <- c('touch', 'taste', 'smell', 'sight', 'sound')

# Make column into factor with those levels:

entro_df <- mutate(entro_df,
                     modality = factor(modality,
                                       levels = level_order))
```

Make a plot of this:

```{r}
# Core of plot:

entro_p <- entro_df %>% 
  ggplot(aes(x = modality,
             y = entropy,
             fill = modality)) +
  geom_boxplot(width = 0.5)

# Add annotations, axes, labels to plot:

entro_p <- entro_p +
  xlab(NULL) +
  ylab('Entropies') +
  scale_fill_viridis_d(option = 'D') +
  scale_y_continuous(limits = c(0, 2),
                     breaks = seq(0, 2, 0.25))

# Cosmetic tweaking:

entro_p <- entro_p +
  theme_classic() +
  theme(legend.position = 'none',
        axis.text.x = element_text(face = 'bold'),
        axis.title = element_text(face = 'bold',
                                  size = 12),
        axis.title.y = element_text(margin = margin(r = 10)))

# Show plot in markdown and also save externally outside of R:

entro_p
ggsave(plot = entro_p,
       filename = '../figures/pdf/target_entropies.pdf',
       width = 5.2, height = 4.5)
ggsave(plot = entro_p,
       filename = '../figures/png/target_entropies.png',
       width = 5.2, height = 4.5)
```

Interesting: taste and smell have the most diffuse profile of targets. Sound the least diffuse — it attaches almost exclusively to sound. Touch has relatively lower entropy than taste and smell, meaning that it tends to latch on to a less diverse range of cells. In fact, the entropy is quite similar to that of sight, probably because what is touch->sound for touch is sight->sound for sight, i.e., they have a distribution that is similarly latched onto a particular modality as preferred target.

Merge metadata back in:

```{r}
entro_df <- left_join(entro_df,
                      select(metadata, table_title, genre, language),
                      by = c('dataset' = 'table_title'))
```

Set priors. We'll make the normal prior for the coefficients a bit more narrow given that the entropy scale is very small.

```{r}
my_priors <- c(prior(normal(0, 1), class = Intercept),
               prior(normal(0, 0.5), class = b),
               prior(student_t(3, 0, 2.5), class = sd), # df = 3, mu = 0, sigma = 2.5
               prior(lkj(2), class = cor))
```

Fit a Gaussian model then:

```{r eval = TRUE}
entropy_mdl <- brm(entropy ~ 
                     # Fixed effects:
                     
                     1 + modality +
                     
                     # Random effects:
                     
                     (1 + modality|language),
                   
                   data = entro_df,
                   family = gaussian,
                   
                   # Priors:
                
                   prior = my_priors,

                   # MCMC settings:
                   
                   seed = 42, cores = 4, chains = 4,
                   iter = 6000, warmup = 4000,
                   control = list(adapt_delta = 0.99),
                   save_pars = save_pars(all = TRUE))

# Save the model:

save(entropy_mdl, file = '../models/entropy_mdl.RData')
```

Load the pre-compiled model:

```{r}
load('../models/entropy_mdl.RData')
```

Assess whether this is a plausible data-generating process:

```{r}
pp_check(entropy_mdl, ndraws = 100)
```

Looks OK.

Check the model:

```{r}
entropy_mdl
```

Get the predictions:

```{r}
entropy_preds <- entropy_mdl |> 
  spread_draws(b_Intercept, b_modalitytaste, b_modalitysmell,
               b_modalitysight, b_modalitysound) |> 
  select(-(.chain:.draw)) |> 
  mutate(touch = b_Intercept,
         taste = b_Intercept + b_modalitytaste,
         smell = b_Intercept + b_modalitysmell,
         sight = b_Intercept + b_modalitysight,
         sound = b_Intercept + b_modalitysound) |> 
  select(-(b_Intercept:b_modalitysound))

# Show:

entropy_preds
```

Perform hypotheses tests with these posterior samples:

```{r}
sum(entropy_preds$touch < entropy_preds$taste) / nrow(entropy_preds)
sum(entropy_preds$touch < entropy_preds$smell) / nrow(entropy_preds)
```

We are very certain that taste and smell attach to a wider range of targets than touch.

Next, let's compare touch to the "higher" senses of sight and sound:

```{r}
sum(entropy_preds$touch > entropy_preds$sight) / nrow(entropy_preds)
sum(entropy_preds$touch > entropy_preds$sound) / nrow(entropy_preds)
```

There is no difference between touch and sight, but touch has more target modality entropy than sound: it attaches to a wider range of targets.

Do taste and smell differ from each other?

```{r}
sum(entropy_preds$taste < entropy_preds$smell) / nrow(entropy_preds)
```

Can't be that certain about any difference.

What about taste and the "higher" senses?

```{r}
sum(entropy_preds$taste > entropy_preds$sight) / nrow(entropy_preds)
sum(entropy_preds$taste > entropy_preds$sound) / nrow(entropy_preds)
```

We can be very certain it has a bigger entropy. Same for smell.

```{r}
sum(entropy_preds$smell > entropy_preds$sight) / nrow(entropy_preds)
sum(entropy_preds$smell > entropy_preds$sound) / nrow(entropy_preds)
```

Yup, same.

And do we have a lot of certainty in sight having higher entropies than sound?

```{r}
sum(entropy_preds$sight > entropy_preds$sound) / nrow(entropy_preds)
```

Yes.

# Entropy plot

Get the posterior samples from the model:

```{r}
posts <- entropy_mdl |> 
  spread_draws(b_Intercept, b_modalitytaste,
               b_modalitysmell, b_modalitysight,
               b_modalitysound)
```

Fill out the regression equation for all five cells of the stats:

```{r}
posts <- posts |> 
  mutate(taste = b_Intercept + b_modalitytaste,
         smell = b_Intercept + b_modalitysmell,
         sight = b_Intercept + b_modalitysight,
         sound = b_Intercept + b_modalitysound) |> 
  rename(touch = b_Intercept) |> 
  select(-(b_modalitytaste:b_modalitysound),
         -(.chain:.draw))

# Show:

posts
```

Compute relevant stats... need to make it long format for that:

```{r}
posts_long <- posts |>
  pivot_longer(cols = touch:sound,
               names_to = 'modality',
               values_to = 'log_ratio') |> 
  arrange(modality)

# Show long format:

posts_long
```

Compute 95% credible interval and means:

```{r}
fixefs <- posts_long |> 
  group_by(modality) |> 
  summarize(lower_CI = quantile(log_ratio, 0.025),
            upper_CI = quantile(log_ratio, 0.975),
            estimate = mean(log_ratio))

# Show:

fixefs
```

Make a beeswarm or violin plot:

```{r}
# Core of plot:

entro_p <- entro_df %>% 
  ggplot(aes(x = modality)) +
  geom_violin(aes(y = entropy),
              alpha = 0,
              color = NA) +
  geom_violin(aes(fill = modality,
                    y = entropy),
              alpha = 0.7,
              linewidth = 0.3) +
  geom_errorbar(data = fixefs,
                mapping = aes(x = modality,
                              ymin = lower_CI, ymax = upper_CI),
                linewidth = 0.45,
                width = 0.15) +
  geom_point(pch = 15, size = 2.2,
             data = fixefs,
             mapping = aes(y = estimate))
NULL

# Add annotations, axes, labels to plot:

entro_p <- entro_p +
  xlab(NULL) +
  ylab('Diversity of targets (entropy)') +
  scale_fill_viridis_d(option = 'D') +
  scale_y_continuous(limits = c(0, 1.75),
                     breaks = seq(0, 1.75, 0.25))

# Cosmetic tweaking:

entro_p <- entro_p +
  theme_classic() +
  theme(legend.position = 'none',
        axis.text.x = element_text(face = 'bold'),
        axis.title = element_text(face = 'bold',
                                  size = 12),
        axis.title.y = element_text(margin = margin(r = 10)))

# Show plot in markdown and also save externally outside of R:

entro_p
ggsave(plot = entro_p,
       filename = '../figures/pdf/entropies_violin_with_95CI.pdf',
       width = 5.2, height = 3.5)
ggsave(plot = entro_p,
       filename = '../figures/png/entropies_violin_with_95CI.png',
       width = 5.2, height = 3.5)
```

# Correlation between ratio and entropy

Check that the two can be merged:

```{r}
all(ratios_long$dataset == entro_df$dataset)
all(ratios_long$modality == entro_df$modality)
```

Correlate the two:

```{r}
both_df <- bind_cols(select(ratios_long, dataset, language, modality, ratio, log_ratio),
                     select(entro_df, entropy))
```

See whether they are correlated, simple correlation that ignores all dependencies:

```{r}
with(both_df,
     cor.test(log_ratio, entropy, method = 'pearson'))
```

What about the averages, are they correlated?

```{r}
both_tab <- both_df |> 
  group_by(modality) |> 
  summarize(mean_ratio = mean(log_ratio, na.rm = TRUE),
            mean_entro = mean(entropy))

both_tab

with(both_tab, cor.test(mean_ratio, mean_entro))
```

Somewhat correlated.

This completes this analysis.



